On exponential sums arising from the classical doubling method

### 2025-04-11 main.tex
Rewrite statement

        \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases. Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w^\ast)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
        \item[B,C,D Case 2)] $w$ is conjugate to an $n$-cycle with one negative:
 In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $w$ on the preimage and by a $2n$ cycle on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n}).$
    \item[$G=\algebraicGroup{U}$ Case 1)] $w$ is conjugate to $(1,2 \hdots n)$ an even cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the product of two $n$ cycles $\begin{pmatrix} 0 & w_nw \\

@@

        \end{pmatrix}$  on the image, and 
		$$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
		where explitely $\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}$ refers to the torus character pair
\left(\begin{pmatrix}
x_0 & 0 & 0 & 0 & \hdots & 0 \\
0 & y_0 & 0 & 0 & \hdots & 0 \\
0 & 0 & F^2(x_0) & 0 & \hdots & 0 \\
0 & 0 & 0 & F^2(y_0) & \hdots & 0 \\
\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
0 & 0 & 0 & 0 & \hdots & F^{n-2}(y_0) \\
\end{pmatrix},\begin{pmatrix}
	F(x_0) & 0 & 0 & 0 & \hdots & 0 \\
	0 & F(y_0) & 0 & 0 & \hdots & 0 \\
	0 & 0 & F^3(x_0) & 0 & \hdots & 0 \\
	0 & 0 & 0 & F^3(y_0) & \hdots & 0 \\
	\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
	0 & 0 & 0 & 0 & \hdots & F^{n-1}(y_0) \\
	\end{pmatrix} \right)
		mapping to $\alpha(x_0)\alpha^{-q}(y_0)$.
    \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} 0 & w_nw \\

@@

        \end{pmatrix}$ on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$

@@

    \exp\left(\innerproduct{x_{T,\theta}}{y}\right) = \theta\left(\aFieldNorm_{\algebraicGroup{T}(\finiteField_m):\algebraicGroup{T}(\finiteField)}\left(y(\zeta_m\right)\right).

@@

The results now follow from these equalities, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition. This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that the coefficient of $q^i$ is $y_{i+1}$ for every $0 \le i \le 2n-1$.

@@

\calvin{end alternate writeup}
\end{comment}
\calvin{start alternate writeup 2 of section 3.4/3.4.1}
\subsection{Stability}\label{subsec:stability}
The goal of this section is to compute $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ proving \Cref{thm:Phi_stable}.

>>>>

        \item (Types B,C,D Case 1) $w$ is conjugate to a cycle of length $n$. \calvin{Add in note about the two type B cases. Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $w$ on the domain and by the cycle $(w,w_n w w_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
        \item (Types B,C,D Case 2) $w$ is conjugate to a cycle of length $n$ with one negative sign.
 In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}$ with $\Frobenius$ acting by $w$ on the domain and by a cycle of length $2n$ on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n}).$
    \item ($\algebraicGroup{G}=\algebraicGroup{U}$ Case 1) $w$ is conjugate to cycle of length $n$, where $n$ is even. In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $-1\cdot w$ on the domain and by the cycle $\left(\begin{smallmatrix} 0 & w_nw \\

@@

        \end{smallmatrix}\right)$ on the image, and 
		$$x_{\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
		Here $\left(\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}\right)$ is realized explicitly as follows. For $z = \left(x,y\right) \in \multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}}$ denote $Dz = \left(\begin{smallmatrix}
			x & 0\\
			0 & y
		\end{smallmatrix}\right) \in \GL_2\left(\finiteFieldExtension{n}\right)$and $$\Frobenius\left(z\right) = \left(\Frobenius x, \Frobenius y\right) = \left(x^q,y^q\right).$$ Then $\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}}$ is realized as the subgroup of $\GL_{2n}\left(\finiteFieldExtension{n}\right) \times \GL_{2n}\left(\finiteFieldExtension{n}\right)$ given by the image of the map $$z \mapsto \left(\diag\left(Dz,D\Frobenius^2 z,\dots, D\Frobenius^{n-2} z\right), \diag\left(D\Frobenius z, D\Frobenius^3 z, \dots, D\Frobenius^{n-1} z\right)\right),$$
		and the character $\alpha \times \alpha^{-q}$ is given by $$z = \left(x,y\right) \mapsto \alpha\left(x\right) \alpha^{-q}\left(y\right).$$
    \item ($\algebraicGroup{G}=\algebraicGroup{\UnitaryGroup}_n$ Case 2) $w$ is conjugate a cycle of length $n$ where $n$ is odd. In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}$ with $\Frobenius$ acting by $-1\cdot w$ on the domain and by the cycle $\left(\begin{smallmatrix} 0 & w_nw \\

@@

        \end{smallmatrix}\right)$ on the image, and $$x_{\multiplicativegroup{\finiteFieldExtension{2n}},\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$

@@

$$
    \exp\left(\innerproduct{x_{T,\theta}}{y}\right) = \theta\left(\aFieldNorm_{\algebraicGroup{T}(\finiteField_m):\algebraicGroup{T}(\finiteField)}\left(y\left(\zeta_m\right)\right)\right).
$$

@@

The results now follow from these equalities, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition. This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that $q^i$ is the coefficient of $y_{i+1}$ in the exponent of the right hand side of the corresponding equation for every $0 \le i \le 2n-1$.

@@

\calvin{end alternate writeup}
\end{comment}

\subsection{Stability}\label{subsec:stability}
The goal of this section is to compute $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ proving \Cref{thm:Phi_stable}.
